Computing Exact Restricted Isometry Constants via Mixed Integer Semidefinite Programming

### 2016-03-18 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
paper: reformulation

The continuous SDPs are solved using the command-line version of
SDPA~7.3.8. We compute the left- and right-hand restricted isometry
constant $\alpha_k$ and $\beta_k$ either exactly using~\eqref{MISDP} or
produce corresponding bounds via~\eqref{Asp07} and~\eqref{Asp08}. In
the latter case, we solve the SDP~\eqref{Asp08Dual} 15 times for $\rho$ between~$0$ and the maximum
diagonal entry of $A\T A$. This is the same approach as in \cite{Asp08},
except that we reduced the number of problems from 25 to 15, as this did
not seem to influence the quality of the solutions much in our preliminary
experiments but brought the solving times more in line with the other
approaches.

>>>>

The continuous SDPs are solved using the command-line version of
SDPA~7.3.8. We compute the left- and right-hand restricted isometry
constant $\alpha_k$ and $\beta_k$ either exactly using~\eqref{MISDP} or
produce corresponding bounds via~\eqref{Asp07} and~\eqref{Asp08}. In
the latter case, we solve the SDP~\eqref{Asp08Dual} 15 times for $\rho$ between~$0$ and the maximum
diagonal entry of $A\T A$. This is the same approach as in \cite{Asp08},
except that we reduced the number from 25 to 15, as this did
not significantly seem to influence the quality of the solutions,
but reduced the solving times.
